p-adic stability in linear algebra

### 2015-01-08 examples/stability.tex
Numerical experiments on LU
Mean and standard deviation for loss in precision over LU factorization.

\noindent
{\bf Numerical experiments.}
\todo{Do it.}

>>>>

\noindent
{\bf Numerical experiments.}
Let $B_n=(E_{1,1},\dots,E_{1,n},\dots,E_{n,1},\dots,E_{n,n})$ be the canonical basis of $M_n(K)$. It can be naturally seen as a basis of $L_n \times U_n.$ For a given $M \in O_n,$ we write $D'(M)$ in $B_n,$ and we can remark that $D'(M)$ is lower-triangular in this basis. We can compute the coordinate-wise loss of precision of $D'(M),$ given by $\sum_u \left( \max_v \left( val(D'(M)_{u,v}) \right) \right),$ and compare it to the lattice-method loss of precision, given by $val(\det(D'(M))).$ The following array sums up the the mean and standard deviation of those losses for 2000 random matrices in $M_d(\mathbb{Z}_2)$ known at precision $100.$

\begin{tabular}{|c|c|c|c|c|}
\hline
 \multirow{2}{*}{ \hspace{0.2cm}$d$\hspace{0.2cm}} & \multicolumn{2}{|c|}{coord-wise method} & \multicolumn{2}{|c|}{lattice method}  \\  \cline{2-5}
  & mean & std & mean & std \\ \hline
$2$ & $-3$& $5$ & $-1.5$ & $1.4$ \\ \hline
$3$& $-9.4$& $11$ & $-2.3$ & $2.3$\\ \hline
$4$ & $-20$& $20$ & $-3.8$ & $3.1$\\ \hline
\end{tabular}
